Marlowe: financial contracts on blockchain

### 2018-05-17 tex/paper.tex
describing the step functions

@@

The type of contracts is given by

@@

The \haskellinline{step} function represents a \emph{single computation step} and has this type:

\begin{haskellcode}
step :: Input -> State -> Contract -> OS -> (State,Contract,AS)
\end{haskellcode}

which is also shown in Figure \ref{fig:step-function}.

The function \haskellinline{step} is wrapped by the \haskellinline{stepAll} function, which calls \haskellinline{step} 
until it stops having any effects. For every block, the \haskellinline{stepBlock} function is called. In addition to 
calling \haskellinline{stepAll}, \haskellinline{stepBlock} will first enable expired cash commitments to be refunded and 
record any choices made at that step.

>>>>

\paragraph{Computations}

Computation is modelled at two different levels.

The \haskellinline{step} function represents a \emph{single computation step} and has this type:
\begin{haskellcode}
step :: Input -> State -> Contract -> OS -> (State,Contract,AS)
\end{haskellcode}
which is also illustrated in Figure \ref{fig:step-function}.

Execution of a contract will involve multiple blocks, with multiple steps in each block. The computation at a single block is given by the \haskellinline{stepBlock} function: this will call the \haskellinline{stepAll} function that calls \haskellinline{step} repeatedly
until it is quiescent. In addition to 
calling \haskellinline{stepAll}, \haskellinline{stepBlock} will first enable expired cash commitments to be refunded and record any choices made at that step. 
The functions \haskellinline{stepAll} and \haskellinline{stepBlock} have the same type as \haskellinline{step} itself.

@@

The type of contracts is given by the Haskell data type

@@
